|

### 2024-08-10 doc/paper.qmd
EM2
do analysis

4. Calculate EM1, which is computed as the Spearman correlation between these scaled changes, aggregated at the country level:
$$
\text{EM2} = \rho\left(\frac{\Delta \text{Accruals}_{it}}{\text{Total Assets}_{i(t-1)}}, \frac{\Delta \text{CFO}_{it}}{\text{Total Assets}_{i(t-1)}}\right)
$$

@@

>>>>

4. Calculate EM2, which is computed as the Spearman correlation between these scaled changes, aggregated at the country level:
$$
\text{EM2} = \rho\left(\frac{\Delta \text{Accruals}_{it}}{\text{Total Assets}_{i(t-1)}}, \frac{\Delta \text{CFO}_{it}}{\text{Total Assets}_{i(t-1)}}\right)
$$

@@

The replication findings regarding EM2 indicate that earnings smoothing is more pronounced in countries like Greece and Japan, while countries like Canada and the United States exhibit less pervasive smoothing behavior, in line with the findings of @Leuz_2003. Despite some differences in magnitude, the overall trends are consistent, reinforcing the idea that earnings smoothing varies significantly across different countries. In fact, these small variations do not significantly alter the overall conclusions. Specifically, the minimum and maximum EM2 values in the replication closely match the original findings, with Greece showing the most earnings smoothing (min: -0.942 vs. -0.928) and Norway the least (max: -0.786 vs. -0.722). This consistency reinforces the accuracy of the replication.
